A performance assessment of evolutionary algorithms in a volunteer computing system

### 2016-03-13 PPSN2016/paper.Rnw
Inserts new table

graph2 & 1173561.5 & 6 & 4 & 761.5 & 22.0 & 0.0520509 & 36 & 73 & 129.04545\\
\hline
reboot & 796214.0 & 9 & 6 & 646.0 & 67.0 & 0.0955121 & 45 & 168 & 75.88889\\
\hline
cachereboot & 392917.0 & 12 & 12 & 576.0 & 79.0 & 0.1575092 & 55 & 225 & 43.28571\\
\hline
\end{tabular}
%% \end{tabular}
%% Initially generated with this code, 
% <<experiments, cache=FALSE,echo=FALSE>>=
%experiment.aggregates$Experiment <- c("base","graph1","graph2","reboot","cachereboot")
%kable(experiment.aggregates)
%@ %def

\end{center}
\end{table}
%
\begin{figure}[htbp]
\centering

@@

>>>>

graph2 & 1173561.5 & 6 & 4 & 761.5 & 22.0 & 0.0520509 & 36 & 73 & 129.04545\\
\hline
reboot & 796214.0 & 9 & 6 & 646.0 & 67.0 & 0.0955121 & 45 & 168 & 75.88889\\
\hline
cachereboot & 392917.0 & 12 & 12 & 576.0 & 79.0 & 0.1575092 & 55 & 225 & 43.28571\\
\hline
\end{tabular}
%% \end{tabular}
%% Initially generated with this code, 
% <<experiments, cache=FALSE,echo=FALSE>>=
%experiment.aggregates$Experiment <- c("base","graph1","graph2","reboot","cachereboot")
%kable(experiment.aggregates)
%@ %def 
\end{center}
\end{table}
%
%
\begin{table}
  \caption{Experiments with overlaps eliminated:  summary of results. \label{tab:filtered}}
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|c|}
\hline
Experiment & Median Time & \multicolumn{2}{|c|}{Median IPs} &\multicolumn{2}{|c|}{Median PUTs} & \#Runs &  Puts/IP \\
&   (ms)        & Total & Used & Total & Used &  & \\
\hline
base & 293685 & 13.0 & 8.0 & 483.0 & 57.0 & 47 & 35.50000\\
\hline
graph1 & 768053 & 12.0 & 5.0 & 601.0 & 79.0 & 21 & 45.84615\\
graph2 & 1477969 & 6.0 & 4.0 & 901.0 & 52.0 & 25 & 149.42857\\
\hline
reboot & 799471 & 9.5 & 6.5 & 656.5 & 67.0 & 44 & 76.48016\\
\hline
cachereboot & 463347 & 12.0 & 12.0 & 638.5 & 80.5 & 52 & 44.25911\\
\hline
\end{tabular}
%% Initially generated with this code, 
%%<<experiments.filtered, cache=FALSE,echo=FALSE>>=
%%experiment.aggregates.filtered$Experiment <- c("base","graph1","graph2","reboot","cachereboot")
%%kable(experiment.aggregates.filtered)
%%@ %def

\end{center}
\end{table}
%
%
\begin{figure}[htbp]
\centering

@@

So we will have to check whether we have effectively eliminated these
overlaps. In order to do that, we will have to establish a threshold
under which reasonably the solution cannot be found. In every
evolutionary algorithm it might happen, by chance, that the solution
is found in just a few evaluations, but that is usually not the
case. By looking at the logs in the last case we have established that
minimun as 16 PUTs; in less than 1600 generations no solution to that
difficult problem will be found. Let us filter then the runs,
eliminating those that use less than 1600 generations to find the
solution which can reasonably be said that they did so because some
browser ``carried over'' a chromosome from the previous run. The
results are shown in Table \ref{tab:filtered}
